\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{fancyhdr}

\title{\textbf{AeroCement Ecosystem: Civilization 2.0}}
\author{Jesse McMillen \\ \texttt{jesseray718@gmail.com}}
\date{\today}

\geometry{margin=1in}

\begin{document}

\maketitle

\section*{Abstract}
Three pillars: Energy (Passive Solar Thermal), Life (Biointensive Permaculture), Shelter (Geodesic Domes). CC-BY-SA/GPL v3. No patents. No monopolies.

\section{Energy}
Solar Thermal Loop with Activated Carbon Aerocement absorber. Output: HEAT + COLD + MECHANICAL + ELECTRICITY.

\section{Life}
Black Locust, Quail Towers, Ferrocement Aquaponics, Seed Banks. Anti-GMO.

\section{Shelter}
Cardboard Geodesic Domes. Acetone-Silicone treatment. Click-flange assembly. Scales: 1V-17V-50V.

\section{License}
CC-BY-SA 4.0 (Hardware) + GPL v3 (Software). Repository: \url{https://github.com/jesseray718/AeroCement_Ecosystem}

% BLOCKCHAIN ANCHOR
\vspace{1cm}
\hrule
\begin{center}
\textbf{SOLANA ANCHOR}\\
TX: \texttt{2fXw4y3pV74zk6pi2dCBTHKJJ69zfvmaRC4ng3sxqY5g9JzNUtdhGrxonL4dHw64TbcVK3C4YqAmskSdow7MYyX8}\\
URL: \url{https://solscan.io/tx/2fXw4y3pV74zk6pi2dCBTHKJJ69zfvmaRC4ng3sxqY5g9JzNUtdhGrxonL4dHw64TbcVK3C4YqAmskSdow7MYyX8}\\
Date: \today
\end{center}
\hrule

\end{document}

\appendix
\section{Verification Disclaimer}
This whitepaper presents engineering concepts requiring local validation:
\begin{itemize}
    \item Thermal efficiency values are theoretical estimates
    \item Material ratios must be tested per local climate/material sourcing
    \item Structural loads require professional engineering review before habitation
    \item Agricultural yields depend on soil, water, and regional conditions
\end{itemize}
This work is licensed for collaborative improvement. Document your results at https://github.com/jesseray718/AeroCement_Ecosystem

\section*{Version History}
v1.0.0 — Initial Publication (\today) \\
Next revision pending experimental validation data.
\end{document}
